Online analysis supplement

### 2021-11-10 index.Rmd
wip

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
itu %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(x = year, y = internet, group = country)) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_wrap(~region, nrow = 2) +
  theme(legend.position = "none")
ggsave(
  "output/Fig-ITU.png", 
  device = agg_png,
  height = 1400, width = 3200, res = 300, units = "px"
)
```

@@

@@

# Fit models in background (need 12 cores)
file_path <- "brm-time-main-effects"
if (!file.exists(file_path)) {
  job::job({
    fit_anx <- brm(
      bf_int + bf_anx + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-anxiety",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms anxiety")
  job::job({
    fit_dep <- brm(
      bf_int + bf_dep + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-depression",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms depression")
  fit_sel <- brm(
    bf_int + bf_sel + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-selfharm",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
  fits_brm_time_main <- tibble(
    outcome = c("Anxiety", "Depression", "Selfharm"),
    fit = list(fit_anx, fit_dep, fit_sel)
  )
  write_rds(fits_brm_time_main, file_path)
} else {fits_brm_time_main <- read_rds(file_path)}
```

@@

# Fit models
file_path <- "brm-time-interactions"
if (!file.exists(file_path)) {
  job::job({
    fit_anx <- brm(
      bf_int + bf_anx + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-anxiety-int2",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms anxiety")
  job::job({
    fit_dep <- brm(
      bf_int + bf_dep + set_rescor(FALSE),
      data = gbd_10,
      file = "output/brm-gbd-time-depression-int2",
      chains = 4,
      cores = 4,
      iter = 1000, warmup = 600, refresh = 10,
      threads = 1,
      control = list(adapt_delta = .9)
    )
  }, title = "Fitting brms depression")
  fit_sel <- brm(
    bf_int + bf_sel + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-selfharm-int2",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
  fits_brm_time_interactions <- tibble(
    outcome = c("Anxiety", "Depression", "Selfharm"),
    fit = list(fit_anx, fit_dep, fit_sel)
  )
  write_rds(fits_brm_time_interactions, file_path)
} else {fits_brm_time_interactions <- read_rds(file_path)}
```

@@

# Fit models in background (need 12 cores)
job::job({
  fit_anx <- brm(
    bf_int + bf_anx + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-internet-anxiety",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms anxiety")
job::job({
  fit_dep <- brm(
    bf_int + bf_dep + set_rescor(FALSE),
    data = gbd_10,
    file = "output/brm-gbd-time-internet-depression",
    chains = 4,
    cores = 4,
    iter = 1000, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms depression")
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
```

>>>>

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
itu %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(x = year, y = internet)) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(
    aes(group = country),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_wrap(~region, nrow = 1) +
  theme(legend.position = "none")
ggsave(
  "output/Fig-ITU.png", 
  device = agg_png,
  height = 600, width = 3200, res = 300, units = "px"
)
```

```{r}
itu %>% 
  mutate(year = make_date(year)) %>%
  mutate(mobile = if_else(mobile > 1.50, NaN, mobile)) %>% 
  pivot_longer(internet:mobile) %>% 
  mutate(name = str_to_title(name)) %>% 
  mutate(name = fct_inorder(name)) %>% 
  ggplot(aes(x = year, y = value)) +
  # coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Users or subscriptions",
    # breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.025, 0.05))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  # Ensure all axes go up to 100%
  geom_blank(
    data = tibble(
      region = "Africa", 
      country = NA, 
      value = 1, 
      year = make_date(2001))
  ) +
  geom_line(
    aes(group = country),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(name~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(2, "pt")
  )
```

@@

### Multiple lines

Here we create two plots. One to show all main variables' time trends for each region, and country within region. Then, show the outcome time trends for top internet trend in each region. Maybe put first in main text and second in appendix.

First, variables with one region per panel.

```{r}
# Add pseudo GWP to figure plot out
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )
p_vars <- bind_rows(
  pseudo_gwp,
  gbd %>% 
    group_by(region, country, year, cause) %>% 
    summarise(mean = mean(val/100))
) %>% 
  ungroup() %>% 
  mutate(cause = fct_inorder(cause)) %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_color_brewer(
    "Variable",
    palette = "Set1", direction = -1
  ) +
  scale_y_continuous(
    "Rate or scale score",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(2, "pt")
  )
p_vars
ggsave(
  "output/Fig-vars-timeseries.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

```{r}
# Get top 1 internet trend country in each region
top_trends <- gbd %>% 
  semi_join(distinct(itu, country)) %>% 
  group_by(region, country) %>% 
  summarise(tidy(lm(internet ~ time, data = cur_data_all()))) %>% 
  filter(term == "time") %>% 
  group_by(region) %>% 
  slice_max(order_by = estimate, n = 1)
pb <- gbd %>% 
  filter(country %in% top_trends$country) %>%
  mutate(country = factor(country, levels = top_trends$country)) %>% 
  mutate(Group = str_glue("{sex} ({age})")) %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, val/100, col = Group)) +
  scale_color_brewer(palette = "Paired") +
  scale_y_continuous(
    "Rate",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~country, scales = "free_y")

(pa + theme(axis.title.x = element_blank())) / 
  pb * 
  theme(panel.spacing = unit(2, "pt")) +
  plot_layout(heights = c(4, 3)) +
  plot_annotation(tag_levels = "A")
ggsave(
  "output/Fig-all-vars-timeseries.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

@@

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_time_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)

Coefficients

```{r}
fits_brm_time_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Revisit figure of temporal trends with coefficients

```{r}
tmp_pars <- fits_brm_time_main %>% 
  mutate(
    out = map2(
      fit, 
      outcome,
      ~hypothesis(
        .x, 
        c(str_glue("{.y}_time = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # Internet trend is estimated in all models keep first
  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
  mutate(across(where(is.numeric), ~round(., 3))) %>% 
  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause = Hypothesis, region = Group, result) %>% 
  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))

p_vars +
  geom_richtext(
    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
ggsave(
  "output/Fig-vars-timeseries-estimates.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

Calculate country coefficients and show scatterplots

```{r time-correlation-anxiety}
# Get average and region
r_region_anxiety <- fit_anx %>% 
  spread_draws(
    b_Anxiety_time, 
    b_internet_time,
    r_region__Anxiety[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_anxiety <- fit_anx %>% 
  spread_draws(
    r_country__Anxiety[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_anx$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_anxiety <- left_join(r_country_anxiety, r_region_anxiety) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    anxiety = b_Anxiety_time + r_region__Anxiety + r_country__Anxiety
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, anxiety)

country_anxiety_ellipse <- spread_draws(
  fit_anx,
  b_Anxiety_time, b_internet_time,
  cor_country__internet_time__Anxiety_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Anxiety_time, 
        y = b_internet_time, 
        z = b_Anxiety_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_anxiety_ellipse <- spread_draws(
  fit_anx,
  b_Anxiety_time, b_internet_time,
  cor_region__internet_time__Anxiety_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Anxiety_time, 
        y = b_internet_time, 
        z = b_Anxiety_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_anxiety_cor <- fit_anx %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Anxiety_time",
      "cor_region__internet_time__Anxiety_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_anxiety_result <- country_anxiety_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_anx <- country_anxiety %>% 
  ggplot(aes(internet, anxiety)) +
  # geom_path(
  #   data = region_anxiety_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_anxiety_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear anxiety trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_anxiety_result %>% 
      filter(variable == "cor_country__internet_time__Anxiety_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r time-correlation-depression}
# Get average and region
r_region_depression <- fit_dep %>% 
  spread_draws(
    b_Depression_time, 
    b_internet_time,
    r_region__Depression[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_depression <- fit_dep %>% 
  spread_draws(
    r_country__Depression[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_dep$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_depression <- left_join(r_country_depression, r_region_depression) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    depression = b_Depression_time + r_region__Depression + r_country__Depression
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, depression)

country_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_country__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_region__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_depression_cor <- fit_dep %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Depression_time",
      "cor_region__internet_time__Depression_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_depression_result <- country_depression_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_dep <- country_depression %>% 
  ggplot(aes(internet, depression)) +
  # geom_path(
  #   data = region_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear depression trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_depression_result %>% 
      filter(variable == "cor_country__internet_time__Depression_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r time-correlation-selfharm}
# Get average and region
r_region_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_time, 
    b_internet_time,
    r_region__Selfharm[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_selfharm <- fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_sel$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, selfharm)

country_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_country__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_region__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_selfharm_cor <- fit_sel %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Selfharm_time",
      "cor_region__internet_time__Selfharm_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_selfharm_result <- country_selfharm_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_sel <- country_selfharm %>% 
  ggplot(aes(internet, selfharm)) +
  # geom_path(
  #   data = region_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear selfharm trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_selfharm_result %>% 
      filter(variable == "cor_country__internet_time__Selfharm_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r}
p_cor_country_anx + theme(axis.title.x = element_blank()) | 
  p_cor_country_dep | 
  p_cor_country_sel + theme(axis.title.x = element_blank())
```

@@

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression-int2",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_time_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_time_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 2) %>% 
  kable_minimal(full_width = FALSE)
```

@@

# Fit models in background (need 12 cores)
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-anxiety",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-depression",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_internet_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_internet_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Different levels

```{r}
# Get average and region
r_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_i1_cw, 
    r_region__Selfharm[region, term]
  ) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term]
    )

# Calculate country coefficients
r_selfharm <- r_selfharm %>% 
  mutate(
    b_average = b_Selfharm_i1_cw,
    b_region = b_average + r_region__Selfharm,
    b_country = b_region + r_country__Selfharm
  )

r_selfharm %>% 
  distinct(.draw, b_average) %>% 
  mutate(region = "Average") %>% 
  ggplot(aes(b_average, region)) +
  stat_halfeye(size = 1, fill = "dodgerblue4") +
  stat_halfeye(
    data = r_selfharm %>% 
      distinct(.draw, region, b_region),
    aes(b_region),
    size = 1, fill = "dodgerblue1"
  ) +
  geom_point(
    data = 
  )
r_selfharm %>% 
  group_by(region, country) %>% 
  median_qi(b_country)
```
